Unrecognized States: A Theory of Self-Determination and Foreign Influence

### 2016-03-02 draft.tex
change time subscripts to superscripts from defn 1 to end of appendix

\begin{enumerate}
	\item The patron invests $R_p^t = \max\left\{\frac{\beta}{1-\de} - \left( Q_{s,t-1} - \mu - L_{s,t-1}\right),0\right\}$ to augment $q_s^t$. Player $c$ invests $R_c^t =0$ in $l_s^t$.

If $R_p^t < \frac{\beta}{1-\de} - \left( Q_{s,t-1} - \mu - L_{s,t-1}\right)$ player $c$ invests $R_c^t = l_s^t - \left(q_s^t + R_p^t \right) + \ve$, for $\ve$ small, in $l_s^t$. Cede becomes the unique best response for the secessionists.

	\item As long as $R_p^t \leq \frac{\nu}{1-\de} + \left( Q_{g,t-1} - L_{g,t-1}\right)$ to augment $l_g^t$, player $c$ invests $R_c^t = R_p^t - \left( Q_{g,t-1} - L_{g,t-1}\right)$ in $q_g^t$. Note that the outcome is that investments in $l_g^t$ and $q_g^t$ are zero.

If $R_p^t > \frac{\nu}{1-\de} + \left( Q_{g,t-1} - L_{g,t-1}\right)$ to augment $l_g^t$, player $c$ invests $R_c^t = 0$. Cede becomes the unique best response for the government.

	\item As long as $R_p^t \leq \frac{1}{p_{1s}} \left[\frac{\nu p_{1s} - \beta (1-p_{1s})}{1 -\de} - \mu + Q_{s,t-1} - \left(-\zeta_{s}(1-\de) + W_{s,t-1}p_{1s} + L_{s,t-1}(1-p_{1s})\right)\right]$ to augment $w_s^t$, player $c$ invests $R_c^t = R_p^tp_{1s} + \mu - Q_{s,t-1} + \left(-\zeta_{s}(1-\de) + W_{s,t-1}p_{1s} + L_{s,t-1}(1-p_{1s})\right)$ in $q_s^t$. Similar to case two, the outcome is that investments in $w_s^t$ and $q_s^t$ are zero.

If $R_p^t > \frac{1}{p_{1s}}\left[\frac{\nu p_{1s} - \beta (1-p_{1s})}{1 -\de} - \mu + Q_{s,t-1} - \left(-\zeta_{s}(1-\de) + W_{s,t-1}p_{1s} + L_{s,t-1}(1-p_{1s})\right)\right] $ to augment $w_s^t$, player $c$ will choose $R_c^t=0$. Fight becomes the unique best response for the secessionists.
\end{enumerate}
\end{definition}

@@

Consider period 1. When Restriction (3) holds, the patron will want to invest just enough to create a buffer of $\frac{\beta}{1-\de}$ between $Q_{s1} \ (= q_{s1} + R_{s1})$ and $l_{s1}$ so that $c$ will not invest. That is, in equilibrium, $R_p^1 = \frac{\beta}{1-\de} -(q_{s1} - l_{s1})$ as long as $p$ can afford to make this investment. Thus we need Restriction (5): $B_p^1 \geq\frac{\beta}{1-\de} - \left(Q_s^0 - \mu - L_s^0 \right)$, where $B_p^1$ is the amount $p$ has available to spend on the conflict in period $1$.

@@

Given that the continuation value from Status Quo is higher than both that from playing Cede and Fight, player $s$ will play Status Quo. The argument for player $g$ is symmetric. \hfill $\blacksquare$
\\
\\
\noindent {\bf Proof of Lemma 2} \\
In the status quo, we have $U_p^t^{SQ}= -R_p^{SQ}$ and $U_c^t^{SQ}= -R_c^{SQ}$. If the outcome is reunification, payoffs in this absorbing state in the period in which the investment is made are $U_p^t^{RU}= -\alpha -R_p^{RU}$ and $U_c^t^{RU}= \beta -R_c^{RU}$ where $SQ$ and $RU$ distinguish investments under the status quo and reunification scenarios respectively.

@@

Player $c$ would be able to induce the secessionists to play Cede---e.g. counter an addition to $q_s^t$ with an investment to $l_s^t$---as long as $R_c^{RU} = \frac{\beta + R_c^{SQ}}{1 -\de} > Q_{s,t-1} -\mu + R_p^t - L_{s,t-1}$.\footnote{Here we assume that the payoff relationship at $t$ is such that ceding is better than fighting. If this relationship is reversed, similar analysis and results hold.} For this to work, the investment required of player $c$ must be no more than the gain player $c$ receives from investing.

On the other hand, if $\frac{\beta + R_c^{SQ}}{1 -\de} \leq Q_{s,t-1} -\mu + R_p^t - L_{s,t-1}$, the patron's investment creates a large enough difference in $Q_s^t - L_s^t$ (net of player $c$'s investment) so that player $c$ will not find contesting the status quo to be in its interest. Whenever the status quo will be the outcome in this way, $c$ maximizes its utility by choice of $R_c^{SQ} =0$.

Restriction (1) combined with equilibrium play implies that  $Q_{s,t-1} > L_{s,t-1}$. Combining this with $R_c^{SQ} =0$, a tighter condition for preventing player $c$ from inducing reunification is $\frac{\beta}{1 -\de} + \mu \leq R_p^t$.

Since the patron is willing to invest up to $\frac{\alpha}{1 -\de}$, $\frac{\beta}{1 -\de} + \mu \leq \frac{\alpha}{1 -\de}$ is a sufficient condition to prevent $c$ from inducing the \emph{reunification} outcome. \hfill $\blacksquare$
\\
\\
\noindent {\bf Proof of Lemma 3} \\
Again, in the status quo, we have $U_p^t^{SQ}= -R_p^{SQ}$ and $U_c^t^{SQ}= -R_c^{SQ}$. If the outcome is recognition of the secessionists, per-period payoffs in this absorbing state become $U_p^t^{REC}= \lambda -R_p^{REC}$ and $U_c^t^{REC}= -\nu -R_c^{REC}$ where $SQ$ and $REC$ distinguish investments under the status quo and recognition scenarios respectively.

@@

If $\frac{\nu}{1-\de} < L_{g,t-1} + R_p^t - Q_{g,t-1}$, the patron's investment in $l_g^t$ creates a large enough difference in $L_s^t - Q_s^t$ (net of player $c$'s investment) so that player $c$ will not find it worthwhile to re-establish the status quo outcome.

On the other hand, player $c$ would be willing to counter whatever investment player $p$ makes to try to induce recognition---e.g. counter an addition to $l_g^t$ with an investment to $q_g^t$---as long as $\frac{\nu}{1-\de} \geq L_{g,t-1} + R_p^t - Q_{g,t-1}$.\footnote{As in the proof of Lemma 2, we have assumed that the payoff relationship at $t$ is such that ceding is better than fighting. If this relationship is reversed, similar analysis and results hold.}

Restriction (1) combined with equilibrium play implies that  $Q_{s,t-1} > L_{s,t-1}$ so that a tighter condition for preventing player $p$ from inducing recognition is $\frac{\nu}{1 -\de} \geq R_p^t$.

@@

This can be expanded as $\frac{\nu p_{1s} - \beta (1-p_{1s})}{1 -\de}  \geq -\zeta_{s}(1-\de) + (W_{s,t-1}+R_p^t)p_{1s} + L_{s,t-1}(1-p_{1s}) - Q_{s,t-1} +\mu = \omega_{s,t-1} - Q_{s,t-1} +R_p^t p_{1s} + \mu$.

Restriction (1) combined with equilibrium play implies that  $Q_{s,t-1} \geq \omega_{s,t-1}$ so a tighter condition for preventing player $p$ from inducing fighting is $\frac{\nu p_{1s} - \beta (1-p_{1s})}{1 -\de} - \mu \geq R_p^t p_{1s}$.

>>>>

\begin{enumerate}
	\item The patron invests $R_p^t = \max\left\{\frac{\beta}{1-\de} - \left( Q_s^{t-1} - \mu - L_s^{t-1}\right),0\right\}$ to augment $q_s^t$. Player $c$ invests $R_c^t =0$ in $l_s^t$.

If $R_p^t < \frac{\beta}{1-\de} - \left( Q_s^{t-1} - \mu - L_s^{t-1}\right)$ player $c$ invests $R_c^t = l_s^t - \left(q_s^t + R_p^t \right) + \ve$, for $\ve$ small, in $l_s^t$. Cede becomes the unique best response for the secessionists.

	\item As long as $R_p^t \leq \frac{\nu}{1-\de} + \left( Q_g^{t-1} - L_g^{t-1}\right)$ to augment $l_g^t$, player $c$ invests $R_c^t = R_p^t - \left( Q_g^{t-1} - L_g^{t-1}\right)$ in $q_g^t$. Note that the outcome is that investments in $l_g^t$ and $q_g^t$ are zero.

If $R_p^t > \frac{\nu}{1-\de} + \left( Q_g^{t-1} - L_g^{t-1}\right)$ to augment $l_g^t$, player $c$ invests $R_c^t = 0$. Cede becomes the unique best response for the government.

	\item As long as $R_p^t \leq \frac{1}{p_{1s}} \left[\frac{\nu p_{1s} - \beta (1-p_{1s})}{1 -\de} - \mu + Q_s^{t-1} - \left(-\zeta_{s}(1-\de) + W_s^{t-1}p_{1s} + L_s^{t-1}(1-p_{1s})\right)\right]$ to augment $w_s^t$, player $c$ invests $R_c^t = R_p^tp_{1s} + \mu - Q_s^{t-1} + \left(-\zeta_{s}(1-\de) + W_s^{t-1}p_{1s} + L_s^{t-1}(1-p_{1s})\right)$ in $q_s^t$. Similar to case two, the outcome is that investments in $w_s^t$ and $q_s^t$ are zero.

If $R_p^t > \frac{1}{p_{1s}}\left[\frac{\nu p_{1s} - \beta (1-p_{1s})}{1 -\de} - \mu + Q_s^{t-1} - \left(-\zeta_{s}(1-\de) + W_s^{t-1}p_{1s} + L_s^{t-1}(1-p_{1s})\right)\right] $ to augment $w_s^t$, player $c$ will choose $R_c^t=0$. Fight becomes the unique best response for the secessionists.
\end{enumerate}
\end{definition}

@@

Consider period 1. When Restriction (3) holds, the patron will want to invest just enough to create a buffer of $\frac{\beta}{1-\de}$ between $Q_s^1 \ (= q_s^1 + R_s^1)$ and $l_s^1$ so that $c$ will not invest. That is, in equilibrium, $R_p^1 = \frac{\beta}{1-\de} -(q_s^1 - l_s^1)$ as long as $p$ can afford to make this investment. Thus we need Restriction (5): $B_p^1 \geq\frac{\beta}{1-\de} - \left(Q_s^0 - \mu - L_s^0 \right)$, where $B_p^1$ is the amount $p$ has available to spend on the conflict in period $1$.

@@

Given that the continuation value from Status Quo is higher than both that from playing Cede and Fight, player $s$ will play Status Quo. The argument for player $g$ is symmetric. \hfill $\blacksquare$
\\
\\
\noindent {\bf Proof of Lemma 2} \\
In the status quo, we have $U_p^{t,SQ}= -R_p^{SQ}$ and $U_c^{t,SQ}= -R_c^{SQ}$. If the outcome is reunification, payoffs in this absorbing state in the period in which the investment is made are $U_p^{t,RU}= -\alpha -R_p^{RU}$ and $U_c^{t,RU}= \beta -R_c^{RU}$ where $SQ$ and $RU$ distinguish investments under the status quo and reunification scenarios respectively.

@@

Player $c$ would be able to induce the secessionists to play Cede---e.g. counter an addition to $q_s^t$ with an investment to $l_s^t$---as long as $R_c^{RU} = \frac{\beta + R_c^{SQ}}{1 -\de} > Q_s^{t-1} -\mu + R_p^t - L_s^{t-1}$.\footnote{Here we assume that the payoff relationship at $t$ is such that ceding is better than fighting. If this relationship is reversed, similar analysis and results hold.} For this to work, the investment required of player $c$ must be no more than the gain player $c$ receives from investing.

On the other hand, if $\frac{\beta + R_c^{SQ}}{1 -\de} \leq Q_s^{t-1} -\mu + R_p^t - L_s^{t-1}$, the patron's investment creates a large enough difference in $Q_s^t - L_s^t$ (net of player $c$'s investment) so that player $c$ will not find contesting the status quo to be in its interest. Whenever the status quo will be the outcome in this way, $c$ maximizes its utility by choice of $R_c^{SQ} =0$.

Restriction (1) combined with equilibrium play implies that  $Q_s^{t-1} > L_s^{t-1}$. Combining this with $R_c^{SQ} =0$, a tighter condition for preventing player $c$ from inducing reunification is $\frac{\beta}{1 -\de} + \mu \leq R_p^t$.

Since the patron is willing to invest up to $\frac{\alpha}{1 -\de}$, $\frac{\beta}{1 -\de} + \mu \leq \frac{\alpha}{1 -\de}$ is a sufficient condition to prevent $c$ from inducing the \emph{reunification} outcome. \hfill $\blacksquare$
\\
\\
\noindent {\bf Proof of Lemma 3} \\
Again, in the status quo, we have $U_p^{t,SQ}= -R_p^{SQ}$ and $U_c^{t,SQ}= -R_c^{SQ}$. If the outcome is recognition of the secessionists, per-period payoffs in this absorbing state become $U_p^{t,REC}= \lambda -R_p^{REC}$ and $U_c^{t,REC}= -\nu -R_c^{REC}$ where $SQ$ and $REC$ distinguish investments under the status quo and recognition scenarios respectively.

@@

If $\frac{\nu}{1-\de} < L_g^{t-1} + R_p^t - Q_g^{t-1}$, the patron's investment in $l_g^t$ creates a large enough difference in $L_s^t - Q_s^t$ (net of player $c$'s investment) so that player $c$ will not find it worthwhile to re-establish the status quo outcome.

On the other hand, player $c$ would be willing to counter whatever investment player $p$ makes to try to induce recognition---e.g. counter an addition to $l_g^t$ with an investment to $q_g^t$---as long as $\frac{\nu}{1-\de} \geq L_g^{t-1} + R_p^t - Q_g^{t-1}$.\footnote{As in the proof of Lemma 2, we have assumed that the payoff relationship at $t$ is such that ceding is better than fighting. If this relationship is reversed, similar analysis and results hold.}

Restriction (1) combined with equilibrium play implies that  $Q_s^{t-1} > L_s^{t-1}$ so that a tighter condition for preventing player $p$ from inducing recognition is $\frac{\nu}{1 -\de} \geq R_p^t$.

@@

This can be expanded as $\frac{\nu p_{1s} - \beta (1-p_{1s})}{1 -\de}  \geq -\zeta_{s}(1-\de) + (W_s^{t-1}+R_p^t)p_{1s} + L_s^{t-1}(1-p_{1s}) - Q_s^{t-1} +\mu = \omega_s^{t-1} - Q_s^{t-1} +R_p^t p_{1s} + \mu$.

Restriction (1) combined with equilibrium play implies that  $Q_s^{t-1} \geq \omega_s^{t-1}$ so a tighter condition for preventing player $p$ from inducing fighting is $\frac{\nu p_{1s} - \beta (1-p_{1s})}{1 -\de} - \mu \geq R_p^t p_{1s}$.
